Verifying Demonstrations

### 2020-02-21 paper/distance-bounding.tex
Improved phrasing for DH and DF
Fixes typo: missing ellipses
Adds definitions for DH/DF from Cristina's model

\begin{definition}[Tainted session, \acs*{DBTF} 
  (strSimTF)~\cite{FormalTerroristFraud}]\label{TaintedTF}
  A time-critical round
  \[\Xscript{\sid}{k, \dotsc, k+2l-1} = (m_k, \dotsc, m_{k+2l-1}),\] for 
  \(l\geq 1\), of an adversary--verifier session~\(\sid\), where \(m_k\) is 
  sent by the verifier, is \emph{tainted} by the round
  \[\Xscript{\sid'}{k, \dotsc, k+2l-1} = (m'_{k}, m'_{k+2l-1})\]
  of a prover--adversary session~\(\sid'\) if
  \begin{align*}
    \marker[\sid, k+2i] &< \marker[\sid', k+2i] \\
    \marker[\sid, k+2i+1] &> \marker[\sid', k+2i+1].
  \end{align*}
\end{definition}

@@

\begin{definition}[Tainted session, \acs*{DBDH}~\cite{TREAD}]%
  \label{TaintedDH}
  \dots
\end{definition}

\begin{definition}[\acs*{DBDH} resistance~\cite{TREAD}]%
  \label{DHresistance}
  \dots
\end{definition}

These definitions for \ac{DBDH} also captures \ac{DBDF} attacks~\cite{TREAD}.

>>>>

\begin{definition}[Tainted session, \acs*{DBTF} 
  (strSimTF)~\cite{FormalTerroristFraud}]\label{TaintedTF}
  A time-critical round
  \[\Xscript{\sid}{k, \dotsc, k+2l-1} = (m_k, \dotsc, m_{k+2l-1}),\] for 
  \(l\geq 1\), of an adversary--verifier session~\(\sid\), where \(m_k\) is 
  sent by the verifier, is \emph{tainted} by the round
  \[\Xscript{\sid'}{k, \dotsc, k+2l-1} = (m'_{k}, \dotsc, m'_{k+2l-1})\]
  of a prover--adversary session~\(\sid'\) if
  \begin{align*}
    \marker[\sid, k+2i] &< \marker[\sid', k+2i] \\
    \marker[\sid, k+2i+1] &> \marker[\sid', k+2i+1].
  \end{align*}
\end{definition}

@@

The final property is \ac{DBDH} and \ac{DBDF}.
The following definitions for \ac{DBDH} also captures \ac{DBDF} 
attacks~\cite{TREAD}.
We first define what the adversary can and cannot do by defining a tainted 
session for \ac{DBDH}.

\begin{definition}[Tainted session, \acs*{DBDH}~\cite{TREAD}]%
  \label{TaintedDH}
  A time-critical round \(\Xscript{\sid}{k, k+1} = (m_k, m_{k+1})\), for some 
  \(k\geq 1\) and \(m_k\) send by the verifier, of an adversary--verifier 
  session \(\sid\) is \emph{tainted} if one of the following conditions holds.
  \begin{itemize}
    \item The maximal \(j\) with \(\Xscript{\sid_{\Commit}}{j} = (\sid, k+1, 
      m_{k+1}')\) for \(m_{k+1}' \neq \Prompt\) and \(\marker{\sid, k} > 
      \marker{\sid_{\Commit}, j}\) satisfies \(m_{k+1}' \neq m_{k+1}\) (or no 
      such \(j\) exists).

    \item The maximal \(j\) with \(\Xscript{\sid_{\Commit}}{j} = (\sid, k+1, 
      m_{k+1}')\) for \(m_{k+1}' = \Prompt\) satisfies \(m_{k+1} \neq 
      m_{k+1}^{\Prompt}\), in which \(m_{k+1}^{\Prompt}\) denotes the message 
      \(m_{k+1}\) in \(\sid_{\Prompt}\).
  \end{itemize}
\end{definition}

To win, the adversary must convince a verifier that he is close when he 
actually is not and without tainting any of the sessions.

\begin{definition}[\acs*{DBDH} resistance~\cite{TREAD}]%
  \label{DHresistance}
  For \iac{DB} authentication scheme~\(\DB\) with \ac{DB} threshold 
  \(t_{\max}\), a \((t, \qp, \qv, \qobs)\)-\ac{DBDH} adversary \(\adv\) wins 
  against \(\DB\) if the verifier accepts \(\adv\) in one of the \(\qv\) 
  adversary--verifier sessions without any critical round being tainted.
  Thus, \ac{DBDH} resistance is defined as the probability 
  \(\Adv_{\DB}^{\text{DH}}(\adv)\) that \(\adv\) wins the game.
\end{definition}
